### 2019-08-27 README.Rmd
added talking point

- Paper
    - Can you re-explain your vision with the minipage format?
- Internship
    - Dixon said he is fine with me switching to 10 hours in the spring (as long as Dr. Caragea agrees)
- Graphics Group
    - email list (should I be added as an admin?)
    - emailed Min (waiting for a response)
    - show updated schedule
    - Susan's idea (could we ask Joe, Erin, and/or Charlotte if they would be interested in preparing this talk?)

>>>>

- Paper
    - Can you re-explain your vision with the minipage format?
- Internship
    - Dixon said he is fine with me switching to 10 hours in the spring (as long as Dr. Caragea agrees)
- Graphics Group
    - email list (should I be added as an admin?)
    - emailed Min (waiting for a response)
    - show updated schedule
    - Susan's idea (could we ask Joe, Erin, and/or Charlotte if they would be interested in preparing this talk?)
    - How to include an image in the preview of a post in blogdown?
